XXX

### 2012-03-23 paper/engNERwiki.tex
A few lines added.

Named Entity Recognition (NER), the task of identifying Named Entities (NEs) in unstructured texts and classifying them into pre-selected classes, is one of the most important subtasks in many NLP tasks, such as Information Retrieval, Information Extraction or Machine Translation. The NER task was introduced with the 6th Message Understanding Conference (MUC) in 1995. In MUC shared tasks the NER consists of three subtasks: entity names, temporal expressions and number expressions. However there is a general agreement in the NER community about the inclusion of temporal expressions and some numerical expressions such as amounts of money and other types of units, the most studied types are names of persons, locations and organizations. The fourth type, called "miscellaneous", is used in the CoNLL NER tasks in 2002 and 2003, and includes proper names falling outside the three classic types. Since then, MUC and CoNLL datasets and annotation schemes have been the major standards applied in the field of NER.

@@

@@

% Introduction: Wikipedia + DBpedia
The corpora are available in the tab separated format used by ConLL (XXX, CITE). In this format, one line contains one word, its linguistic features and the named entity tags. Sentence boundaries are marked by empty lines. The linguistic features include the lemmatized form of the word, part-of-speech tag and chunk tag. Two named entity tags are included with each word: one is the most specific DBpedia category it belongs to, if any; the other is the ConLL named entity tag. While the named entity tags can be considered "gold", the linguistic features are provided on a "best-effort" basis (XXX: check the LREC paper to find a better wording for this).
XXX: past or present tense?

We decided to use Wikipedia because

The categories of Wikipedia are too numerous and ; not a tree;

@@

While the correspondence described above holds for most classes in the XXX sub-hierarchies, there are some exceptions. For instance, the class \texttt{SportsLeague} is part of the \texttt{Organisation} sub-hierarchy, but in the ConLL corpus, sport leagues are tagged as MISC. Similarly, the class \texttt{SportsTeamSeason} is under \texttt{Event}, by which account it would be classified as MISC; however, ConLL does not recognize such entities. To account for these misclassification, as well as the miscellaneous classes outside the main hierarchies, we have introduced a mapping mechanism. We created a file of DBpedia class -- NER category mappings. Whenever an entity is evaluated, we look up its class, as well as the ancestors of its class, in the mapping, and assign to the entity the category of the class that matches it most closely -- i.e. the category of the entity's class, if it is in the list, or that of its closest ancestor. XXX!!! If no match is found, the entity is tagged with \texttt{0}. Since we take advantage of the inheritance hierarchy, the mapping list remains short: it contains only the root classes of the main sub-hierarchies, exceptions of the like XXX mentioned above and the various classes that belong to the MISC category according to the ConLL annotation guideline.

As of version 3.7, the DBpedia ontology allows multiple superclasses, making the hierarchy a directed acyclic graph. This introduces the problem of selecting the right superclass, and hence, ConLL mapping for classes with more than one parent. In version 3.7, the only such class is \textit{Library}, which can be traced back to both \textit{Place} and \textit{Organisation}. There are two ways to tackle this problem. The first is to follow the DBpedia guidelines and only retain the first parent. The second method is manually deciding the right NER mapping for the ambiguous XXX class and adding it to the mapping file. The first approach, unfortunately, already fails to assign the correct ConLL NER tag to our only example. The reason behind this failure is that multiple parents in an ontology show an inherent ambiguity in the class in question: it is entirely natural to think of a library as a location as well as a public organization. DBpedia's guidelines prefers Organisation; ConLL's LOC. Therefore, only the second, manual approach ensures correct tagging. XXX

@@

\subsection{Remarks}

In this paper, we describe % not only ConLL? Do we need this?

@@

@@

a nyelv és népnevek magyarul nem NE-k, vagyis nem kell az annotálásukkal foglalkozni

@@

a tulajdonnevekből képzett szavak sem NE-k

@@

@@

\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
Alfred~V. Aho and Jeffrey~D. Ullman.
\newblock 1972.
\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
\newblock Prentice-{Hall}, Englewood Cliffs, NJ.

\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
{American Psychological Association}.
\newblock 1983.
\newblock {\em Publications Manual}.
\newblock American Psychological Association, Washington, DC.

\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
{Association for Computing Machinery}.
\newblock 1983.
\newblock {\em Computing Reviews}, 24(11):503--512.

\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
\newblock 1981.
\newblock Alternation.
\newblock {\em Journal of the Association for Computing Machinery},
  28(1):114--133.

\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
Dan Gusfield.
\newblock 1997.
\newblock {\em Algorithms on Strings, Trees and Sequences}.
\newblock Cambridge University Press, Cambridge, UK.

>>>>

Named Entity Recognition (NER), the task of identifying Named Entities (NEs) in unstructured texts and classifying them into pre-selected classes, is one of the most important subtasks in many NLP tasks, such as Information Retrieval, Information Extraction or Machine Translation. The NER task was introduced with the 6th Message Understanding Conference (MUC) in 1995 (CITE). In MUC shared tasks the NER consists of three subtasks: entity names, temporal expressions and number expressions. However there is a general agreement in the NER community about the inclusion of temporal expressions and some numerical expressions such as amounts of money and other types of units, the most studied types are names of persons, locations and organizations. The fourth type, called "miscellaneous", is used in the CoNLL NER tasks in 2002 and 2003 (CITE), and includes proper names falling outside the three classic types. Since then, MUC and CoNLL datasets and annotation schemes have been the major standards applied in the field of NER.

@@

\section{Corpus Description}

% TODO: pls írd meg az első pár mondatot és nevezd át a sectiont!

The corpora are available in the tab separated format used by ConLL (XXX, CITE). In this format, one line contains one word, its linguistic features and the named entity tags. Sentence boundaries are marked by empty lines. The linguistic features include the lemmatized form of the word, its part-of-speech and chunk tags. Two named entity tags are included with each word: one is the most specific DBpedia category it belongs to, if any; the other is the ConLL named entity tag. While the named entity tags can be considered "silver", the linguistic features are provided on a "best-effort" basis.

The corpus is available under the Creative Commons Attribution-Sharealike 3.0 Unported License (CC-BY-SA), the same license under which the text of Wikipedia is released. The data files can be freely downloaded from ...\footnote{To be filled in in the camera-ready version.}.

@@

% Introduction: Wikipedia + DBpedia

@@

While the correspondence described above holds for most classes in the XXX sub-hierarchies, there are some exceptions. For instance, the class \texttt{SportsLeague} is part of the \texttt{Organisation} sub-hierarchy, but in the ConLL corpus, sport leagues are tagged as MISC. Similarly, the class \texttt{SportsTeamSeason} is under \texttt{Event}, by which account it would be classified as MISC; however, ConLL does not recognize such entities. To account for these misclassification, as well as the miscellaneous classes outside the main hierarchies, we have introduced a mapping mechanism. We created a file of DBpedia class -- NER category mappings. Whenever an entity is evaluated, we look up its class, as well as the ancestors of its class, in the mapping, and assign to the entity the category of the class that matches it most closely -- i.e. the category of the entity's class, if it is in the list, or that of its closest ancestor. XXX!!! If no match is found, the entity is tagged with \texttt{O}. Since we take advantage of the inheritance hierarchy, the mapping list remains short: it contains only the root classes of the main sub-hierarchies, exceptions of the like XXX mentioned above and the various classes that belong to the MISC category according to the ConLL annotation guideline.

As of version 3.7, the DBpedia ontology allows multiple superclasses, making the hierarchy a directed acyclic graph (CITE). This introduces the problem of selecting the right superclass, and hence, ConLL mapping for classes with more than one parent. In version 3.7, the only such class is \textit{Library}, which can be traced back to both \textit{Place} and \textit{Organisation}. There are two ways to tackle this problem. The first is to follow the DBpedia guidelines and only retain the first parent. The second method is manually deciding the right NER mapping for the ambiguous XXX class and adding it to the mapping file. The first approach, unfortunately, already fails to assign the correct ConLL NER tag to our only example. The reason behind this failure is that multiple parents in an ontology show an inherent ambiguity in the class in question: it is entirely natural to think of a library as a location as well as a public organization. DBpedia's guidelines prefers Organisation; ConLL's LOC. Therefore, only the second, manual approach ensures correct tagging. XXX

@@

@@

In addition to differences in grammar,

The Szeged NER guideline relies heavily on the rules of capitalization to decide which words should be marked as named entities. In Hungarian, apart from the first word in the sentence, only proper nouns are capitalized.
Thus, the following concepts are not considered named entities in Hungarian XXX:
\begin{itemize}
\item Names of languages and ethnic groups
\item Words created from proper nouns through derivation, most prominently
\item Adjectival form of location names
\item Months % angolban sem
\end{itemize}

@@

@@

@@

% Hun -> not utf-8, loss of precision?

@@

\bibitem[\protect\citename{Bizer \bgroup et al.\egroup}2009]{Bizer:09} 
Christian Bizer, Jens Lehmann, Georgi Kobilarov, Sören Auer, Christian Becker, Richard Cyganiak, Sebastian Hellmann.
\newblock 2009.
\newblock DBpedia -- A Crystallization Point for the Web of Data. 
\newblock In: {\em Journal of Web Semantics: Science, Services and Agents on the World Wide Web}, Issue 7, pages 154--165.
